method

### 2021-12-03 06_Paper/ER-ED/method.Rmd
added ANOVA for effort

aov.arousal = afex::aov_ez(id = "ID",    #ATTENTION: needs pagacke "afex"
                      dv = "arousal",
                      data = data_ER,
                      within = "block",
                      fun_aggregate = mean) 
afex::nice(aov.arousal, es = "pes")

# compute posthoc tests for both within measures
posthoc_test_strategy = emmeans::emmeans(aov.arousal$aov, specs = "block")
pairs(posthoc_test_strategy, adjust = "bonferroni")
```

>>>>

aov.arousal = afex::aov_ez(id = "ID",
                           dv = "arousal",
                           data = data_ER,
                           within = "block",
                           fun_aggregate = mean) 
afex::nice(aov.arousal, es = "pes")

# compute posthoc tests for within measures
posthoc_arousal = emmeans::emmeans(aov.arousal$aov, specs = "block")
pairs(posthoc_arousal, adjust = "bonferroni")

# ANOVA subjective effort ratings

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = data_ER,
                          within = "block",
                          fun_aggregate = mean)

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
pairs(posthoc_effort, adjust = "bonferroni")
```
